Group 5 Report

### 2022-08-03 Report/Group 5 report v2.Rmd
Update brainstorming and data

OPX wanted us to harvest the organisations' financial data from the web.
During the first stage of brainstorming, we wanted to find a simple and
automated way to do so.

We discussed creating web scraping code that could collect data across
different websites, but quickly decided that this would be too
difficult, and that it would only work with selected organisations. The next
suggested solution was to create code that could read PDF documents
that OPX downloaded themselves. Our code would analyse and organise the
uploaded data from the PDF documents.

However, different organisations publish financial data in different
ways in their annual reports -- some financial statements were included
as tables, some as pictures, etc. This led us to phase 2.

@@

```{r, echo=FALSE, fig.cap="Need caption"}
knitr::include_graphics("Images/lagret_tekst.png") # må finne ut av hvordan vi deler disse bildene

# inkluder en med årsregnskapet som pdf her
```

@@

At this stage, we wanted to explore alternatives to analysing PDF
documents. We discussed how to do so, and concluded that we had three
options:

- Financial statements in annual report PDF documents. 
- Web scrape Proff.no for financial statements. 
- Web scrape the Brønnøysund registry.

We divided the task among ourselves to explore whether these solutions
were feasible or not. The first option of using PDF documents still had
the issue of financial statements not always being published as text, as well as their often wildly differing formats. Unfortunately, we quickly found that Proff.no disallows any automated collection of data from their website. The Brønnøysund registry does offer API access to all the financial statements, but we discovered that access currently costs NOK 480,000.

We started to look at workarounds for this problem. It could still be
possible to download Proff.no HTML websites manually for each
organisation. We did receive some XML files from Statistics Norway, but using these is ultimately not a viable solution for OPX.

The Brønnøysund registry and Proff.no had different divisions of
accounting items than the ones OPX wanted. We found that we needed to
create an item path from the webpage items to the OPX items, and we
attempted to do so in Excel at first, so that we later could code this
into R. While doing so, we realised that it would be practically
impossible to extract the correct sums for the OPX accounting items from
the Brønnøysund items. This was e.g. because OPX had split the operating
income into public and private contributions, while the Brønnøysund
registry and Proff.no had not.

```{r, echo=FALSE, fig.cap="Need caption", fig.align='center'}
knitr::include_graphics("Images/info_kreft.png")
```

```{r, echo=FALSE, out.width="100%", fig.cap="Need caption"}
knitr::include_graphics("Images/regnskapssti.png")
```

When also discovering that not all organisations publish their financial
statements, and certainly not for every year, we decided to give up on
collecting financial data for OPX, as the task turned out to impossible given current reporting requirements and practices. This is when we moved on to the third
and final stage.

@@

The OPX case requested two tasks -- web scrape financial data, and create
KPIs. During phase three, we scrapped all ideas and progress from the
first two stages, and focused on creating KPIs.

@@

In order to create a somewhat more challenging task for ourselves, we
also decided to create an interactive dashboard based on Shiny that OPX could use, which would
display the KPIs as well as financial trends for the selected
organisation. To use this, OPX needs to gather the financial data
themselves, as well as download data manually from Proff.no, and then upload this into the dashboard in the form of Excel and HTML documents.

@@

We wanted to use web scraping to collect the data, so that we could have
automated the data input process. As described, we explored different
potential solutions. We experimented on coding such that data could have
been imported from XML files. However, once we realised that the available
financial data was of little use, this experimentation stopped.

@@

We copied these financial statements manually into an Excel document.
Perhaps a 'simple' solution, however our code requires OPX to import
both an Excel document themselves into shiny, as well as a HTML document
from Proff.no.

@@

>>>>

OPX wanted us to harvest the organizations' financial data from the web.
During the first stage of brainstorming, we wanted to find a simple and
automated way to do so.

We discussed creating a webcrawler that could collect data across
different websites, but quickly decided that this would be too
difficult, and that it would only work with selected organizations. The
suggested solution was to create a code that could read PDF documents
that OPX downloaded themselves. Our code would analyze and organize the
uploaded data from the PDF documents.

However, different organizations publish financial data in different
ways in their yearly reports -- some financial statements were included
as tables, some as pictures, etc. This led us to phase 2.

@@

```{r, echo=FALSE, fig.cap="Need caption"}
# Illustration some text some pictures in financial statements
knitr::include_graphics("Images/lagret_tekst.png") # Kreftforeningen 201?
knitr::include_graphics("Images/lagret_bilde.png") # Regnskogfondet 2018
```

@@

At this stage, we wanted to explore alternatives to analyzing PDF
documents. We discussed how to do so, and concluded that we had three
options: 
- Financial statements in yearly report PDF documents. 
- Webscrape Proff.no for financial statements. 
- Webscrape the Brønnøysund registry.

We divided the task among ourselves to explore whether these solutions
were feasible or not. The first option of using PDF documents still had
the issue of financial statements not always being published as text.
Also, we quickly found that Proff.no disallowed webscraping on their
website. The Brønnøysund registry did store downloadable XML documents
of all the financial statements on their website, but we discovered that
access to these files cost about half a million NOK.

We started to look at workarounds for this problem. It would still be
possible to download Proff.no HTML websites manually for each
organization. And, we attempted to request a temporary access to the
Brønnøysund registry's XML documents.

The Brønnøysund registry and Proff.no had different divisions of
accounting items than the ones OPX wanted. We found that we needed to
create an item path from the webpage items to the OPX items, and we
attempted to do so in Excel at first, so that we later could code this
into R. While doing so, we realized that it would be practically
impossible to extract the correct sums for the OPX accounting items from
the Brønnøysund items. This was e.g. because OPX had split the operating
income into public and private contributions, while the Brønnøysund
registry and Proff.no had not.

```{r, echo=FALSE, fig.cap="Need caption", fig.align='center'}
# Illustration brns vs OPX accounting items
knitr::include_graphics("Images/Brns_items.png")
knitr::include_graphics("Images/OPX_items.png")
knitr::include_graphics("Images/Marriage.png")
```

When also discovering that not all organizations publish their financial
statements, and certainly not for every year, we decided to give up on
collecting financial data for OPX. This is when we moved on to the third
and final stage.

```{r, echo=FALSE, out.width="100%", fig.cap="Need caption"}
# Illustration only published for some years example
knitr::include_graphics("Images/Regnskogfondet_stops2018.png")
knitr::include_graphics("Images/Kreftforeningen_starts2019.png")
```

@@

The OPX case requested two tasks -- webscrape financial data, and create
KPIs. During phase three, we scrapped all ideas and progress from the
first two stages, and focused on creating KPIs.

@@

In order to create a somewhat more challenging task for ourselves, we
also decided to create an interactive dashboard that OPX could use, which 
would display the KPIs as well as financial trends for the selected
organization. To use this, OPX needs to gather the financial data
themselves, then upload this into the shiny app as an excel and an 
html document.

@@

We wanted to use webscraping to collect the data, so that we could have
automated the data input process. As described, we explored different
potential solutions. We experimented on coding such that data could have
been imported from XML files. However, once we realized that the
financial data was of little use, this experimentation stopped.

@@

We copied these financial statements manually into an Excel document.
Perhaps a "simple" solution, however our code requires OPX to import
both an Excel document themselves into shiny, as well as a HTML document
from Proff.no.

```{r, echo=FALSE, out.width="100%", fig.cap="Need caption"}
# Bilde av den "endelige" excel-versjonen som brukes til å laste inn i shiny
knitr::include_graphics("Images/Excel_final.png")
```

@@

ur data was gathered from OPXs own web page, and from Proff.no. As described 
in the previous parts, we wanted to gather data from the yearly reports or by 
scraping the Brønnøyund registry or Proff.no, but found this to be close to 
impossible. The data used is the one that OPX has gathered themselves directly 
from the organizations. This data was also used to test that our codes in R 
were correct.

We have also used Proff.no to visualize the annual incomes and some KPIs. 
This is data that the organizations have reported themselves to Proff.no. 
Since there are no regulations regarding reporting data for NGOs in Norway, 
the organizations have not been consistent with the data reporting. This 
explains the holes in the presented data.
